An alternative MIP formulation for the Military Flight and Maintenance Planning problem

### 2020-10-07 R/presentations/thesis_defense/presentation.Rmd
thesis defense ppt and dassault documentation.

---
title: "An alternative MIP formulation for the Military Flight and Maintenance Planning problem"
author: |
    | Franco Peschiera, Alain Haït, Olga Battaïa, Nicolas Dupin
    | \tiny (franco.peschiera@isae-supaero.fr)
date: "February, 2020"
output:
  xaringan::moon_reader:
    css: ["footer-header.css", "default"]
    self_contained: false
    lib_dir: libs
    nature:
      highlightStyle: github
      countIncrementalSlides: false
    footer: "ISAE-SUPAERO, Université de Toulouse, France"
  slidy_presentation:
    css: ./../../../css/baobab_slidy.css
    incremental: yes
    footer: "ISAE-SUPAERO, Université de Toulouse, France"
    toc: true
  beamer_presentation:
    theme: "Berlin"
    toc: true
    slide_level: 2
    incremental: yes
    fig_height: 4
    includes:
        in_header: header.tex
editor_options: 
  chunk_output_type: console
---

@@

### Problem (informally)

Assign both **missions** and **maintenance operations** to a fleet of aircraft in order to maximize availability and minimize costs. **Missions** have fixed start and end times and have particular needs in terms of aircraft and flight hours. **Maintenance operations** have specific rules that govern their frequency and capacity.

.center[
```{r, echo=FALSE, out.width='100%', warning=FALSE}
knitr::include_graphics('calendar3.png')

```
]

@@

* A series of $j \in \mathcal{J}$ pre-scheduled missions are planned along a horizon divided into $t \in \mathcal{T}$ periods.
* Each mission requires a certain **number** $R_{j}$ of aircraft $i \in \mathcal{I}$ which it employs for $H_j$ **hours** in each period.
* The heterogeneous fleet requires recurrent preventive maintenance operations (**checks**).
* A check takes exactly $M^d$ periods and cannot be interrupted. There is a limited **capacity** for maintenances at each period.
* The objective is to **minimize the total number of checks** while **maximizing the status of the fleet** at the end of the horizon.

**Other**: soft constraints on the state of the fleet at each period, initial conditions, default consumption, reduce variance of frequency of checks.

@@

### State of the art

* FMP: Flight and Maintenance Planning problem.
* In `r Citep(myBib, "Cho2011")`, US Army aircraft were assigned daily operations over a year to aircraft in order to minimize the maximum number of maintenances.
* In `r Citep(myBib, "Kozanidis2008")`, Greek aircraft had monthly assignments of maintenances and flight hours in order to maximize the availability and final state of squadrons.
* In `r Citep(myBib, "Verhoeff2015")`, monthly assignments were done and several objectives were taken into account: availability, serviceability and final state.
* In `r Citep(myBib, "Seif2018")`, a generalization for different types of maintenances and capacities was done.
* In `r Citep(myBib, "Peschiera2019")`, the problem was proved NP-Complete.

@@

### Previous formulation

>>>>

---
title: "An alternative MIP formulation for the Military Flight and Maintenance Planning problem"
author: |
    | Franco Peschiera, Alain Haït, Olga Battaïa, Nicolas Dupin
    | \tiny (franco.peschiera@isae-supaero.fr)
date: "February, 2020"
output:
  beamer_presentation:
    theme: "Berlin"
    toc: true
    slide_level: 2
    incremental: yes
    fig_height: 4
    includes:
        in_header: header.tex
  slidy_presentation:
    css: ./../../../css/baobab_slidy.css
    incremental: yes
    footer: "ISAE-SUPAERO, Université de Toulouse, France"
    toc: true
  xaringan::moon_reader:
    css: ["footer-header.css", "default"]
    self_contained: false
    lib_dir: libs
    nature:
      highlightStyle: github
      countIncrementalSlides: false
    footer: "ISAE-SUPAERO, Université de Toulouse, France"
editor_options: 
  chunk_output_type: console
---

@@

### Context

Maintenance, maintenance planning. Flight and maintenance planning. Military. DGA et armée de l'air.

@@

Present the industrial problem for the Mirage 2000.

@@

### Contributions

1. Complexity proof and exact methods.
2. Pattern-like modeling and machine learning.
3. Efficient pattern-generation with DP.

@@
